### 2021-01-31 research project/sections/Background.tex
rp

Which has come to be known as the Leibniz formula for $\pi$, after the German mathematician 
who discovered the same formula two decades later \cite{edwards_1994}

@@

This can be expressed in mathematical terms as such:

@@

These expressions, when under a single expression result in the aforementioned 
formula with nested roots.

>>>>

Which has come to be known as the Leibniz formula for $\pi$, after the German mathematician 
who discovered the same formula two decades later. \cite{edwards_1994}

@@

This can be expressed in mathematical terms as such, where we let $c$ be the circumference of 
a circle of diameter $d$:

$c = \sqrt{12 d^2} - \frac{\sqrt{12 d^2}}{3 \cdot 3} + \frac{\sqrt{12 d^2}}{3^2 \cdot 5} - \frac{\sqrt{12 d^2}}{3^3 \cdot 7} + \dots$

And since $c = \pi d$, for a circle of diameter 1, $c = \pi$, all $d$ terms cancel and 
the expression can be factorized as:

$c = \pi = \sqrt{12} ( 1 - \frac{1}{3 \cdot 3} + \frac{1}{3^2 \cdot 5} - \frac{1}{3^3 \cdot 7} + \dots )$

Or as an infinite sum:

$\pi = \sqrt{12} \sum\limits_{n=0}^\infty \frac{(-3)^{-n}}{2n+1}$

@@

### 2021-01-31 research project/sections/Computational_approach.tex
rp

The \verb|mpmath| library was used for the floating point operations required 
for comparison between approximated values and the constant $\pi$ that wouldn't 
have been possible using standard Python libraries \cite{mpmath}.

>>>>

The \verb|mpmath| library was used for the floating point operations required 
for comparison between approximated values and the constant $\pi$ that wouldn't 
have been possible using standard Python libraries. \cite{mpmath}
